### 2010-02-15 trunk/deliverables/D5_1_2/fast_d5_1_2.tex
UPDATE: text about linked data and changes to building blocks structures
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@554 d8b0c59b-6544-0410-94d9-83a5658a058e

\begin{itemize}
	\item Section~\ref{sec:installation_guide}. Installation Guide describes a set of steps to be followed in order to install and execute the FAST Catalogue. Also some configuration instructions are specified.
	\item Section~\ref{sub:content_negotiation}. Content Negotiation states how the FAST Catalogue has adopted several of the content negotiation principles.
	\item Section~\ref{sec:restful_catalogue_api}. RESTful Catalogue API has been intensively extended and modified in order to  reflect all the new functionality and how every request or response is constructed. Some of the most important features added in this iteration are:
	\begin{itemize}
		\item support for form elements, operators and back-end services (see Section ...),
		\item convenience operations for recommendation and checking satisfaction and reachability for form elements, operators and back-end services (see Section ...),
		\item and, last but not least, support for Screen planning (see Section~\ref{sub:planning}).
	\end{itemize}
	\item Several appendixes have been added with the JSON structure of every building block the Catalogue can deal with.
	\item Appendix A. Last year an evaluation to choose the best technology for the Catalogue was done. It was not included in any formal deliverable, so this year it has been documented as an appendix.
\end{itemize}

@@

@@

Independently the type of repository, the parameter \emph{serverURL} needs to take the value of the URL where the FAST Catalogue instance has been deployed. If you are testing the application in your machine, it may be something like \url{http://localhost:8080/FASTCatalogue}.

@@

It is recommended to check if the FAST Catalogue has been successfully installed. To do that, a simple HTTP request, using a Web browser, can be sent to the URL the Catalogue is deployed, and specifying a type of resource such as Screen. The URL would be similar to \url{http://localhost:8080/FASTCatalogue/screens}. Depending on the variant chosen, the response may be different. For JSON, the response should be \verb|[]|, but in HTML the message \verb|No screens found.| should be shown.

@@

\singlespacing
\begin{verbatim}
{
  "canvas": [
    { "uri": "http://localhost:8080/catalogue/screens/238" },
    { "uri": "http://localhost:8080/catalogue/screens/323" }
  ],
  "elements": [
    { "uri": "http://localhost:8080/catalogue/screens/636" }
  ],
  "domainContext": {
    "tags": [
      {
        "label": { "en-GB": "Amazon" },
        "means": "http://dbpedia.org/page/Amazon.com"
      }
    ],
    "user": "irivera",
  },
  "criterion": "reachability"
}
\end{verbatim}
\doublespacing

@@

\subsection{Content Negotiation} % (fold)
\label{sub:content_negotiation}

@@

In summary, the basic idea of content negotiation, as stated in the HTTP 1.1 specification ~\cite{http1.1}, is to serve the best variant for a resource, taking into account what variants are available, what variants the server may prefer to serve, what the client can accept, and with which preferences: in HTTP, this is done by the client which may send, in its request, Accept headers (Accept, Accept-Language and Accept-Encoding), to communicate its capabilities and preferences in Format, Language and Encoding, respectively.

In fact, what the catalogue really does is "format negotiation" since the alternate representationos are just based on the selection of the media type, through the Accept header, but does not consider different languages or encoding types. The formats supported are JSON, RDF+XML and HTML.

@@

To create a new screen, a POST request is send to the catalogue server, including the JSON representation of the screen as the body of the request:

@@

\singlespacing
\begin{verbatim}
{
  "code": "http://demo.fast.morfeo-project.org/code/amazonList.js",
  "creationDate": "2010-01-26T17:01:13+0000",
  "creator": "irivera",
  "description": {"en-gb": "Please fill the description..."},
  "homepage": "http://fast.morfeo-project.eu/",
  "icon": "http://demo.fast.morfeo-project.org/images/amazonList.png",
  "id": "28",
  "label": {"en-gb": "Prueba1"},
  "name": "ProductList",
  "postconditions": [
    [
      {
        "id": "item",
        "label": { "en-gb": "An item" },
        "pattern": "?I
                    http://www.w3.org/1999/02/22-rdf-syntax-ns#type
                    http://aws.amazon.com/AWSECommerceService#Item",
        "positive": "true"
      }
    ]
  ],
  "preconditions": [
    [
      {
        "id": "filter",
        "label": { "en-gb": "A search criteria" },
        "pattern": "?F
                    http://www.w3.org/1999/02/22-rdf-syntax-ns#type
                    http://aws.amazon.com/AWSECommerceService#SearchCriteria",
        "positive": "true"
      }
    ]
  ],
  "rights": "http://creativecommons.org/",
  "screenshot": "http://demo.fast.morfeo-project.org/images/amazonProductList.png",
  "tags": [{"label": {"en-gb": "amazon"}}],
  "type": "screen",
  "uri": "http://localhost:8080/catalogue/screens/28",
  "version": "0.1"
}
\end{verbatim}
\doublespacing

@@

\singlespacing
\begin{verbatim}
[
  {
    "code": "http://demo.fast.morfeo-project.org/code/amazonList.js",
    "creationDate": "2010-01-26T17:01:13+0000",
    "creator": "irivera",
    "description": {"en-gb": "Please fill the description..."},
    "homepage": "http://fast.morfeo-project.eu/",
    "icon": "http://demo.fast.morfeo-project.org/images/amazonList.png",
    "id": "28",
    "label": {"en-gb": "Prueba1"},
    "name": "ProductList",
    "postconditions": [
      [
        {
          "id": "item",
          "label": { "en-gb": "An item" },
          "pattern": "?I
                      http://www.w3.org/1999/02/22-rdf-syntax-ns#type
                      http://aws.amazon.com/AWSECommerceService#Item",
          "positive": "true"
        }
      ]
    ],
    "preconditions": [
      [
        {
          "id": "filter",
          "label": { "en-gb": "A search criteria" },
          "pattern": "?F
                      http://www.w3.org/1999/02/22-rdf-syntax-ns#type
                      http://aws.amazon.com/AWSECommerceService#SearchCriteria",
          "positive": "true"
        }
      ]
    ],
    "rights": "http://creativecommons.org/",
    "screenshot": "http://demo.fast.morfeo-project.org/images/amazonProductList.png",
    "tags": [{"label": {"en-gb": "amazon"}}],
    "type": "screen",
    "uri": "http://localhost:8080/catalogue/screens/28",
    "version": "0.1"
  },
  {
    "creationDate": "2009-02-07T09:59:52+0000",
    "creator": "fabio",
    ...,
	  "uri": "http://localhost:8080/catalogue/screens/14",
    "version": "1.0"
  },
  {
    "creationDate": "2009-02-07T09:59:52+0000",
    "creator": "javier",
    ...,
	  "uri": "http://localhost:8080/catalogue/screens/564",
    "version": "1.0"
  }
]
\end{verbatim}
\doublespacing

@@

Following is shown an example of usage of this operation considering a canvas with the screen \texttt{http://localhost:8080/catalogue/screens/654}.

\singlespacing
\begin{verbatim}
{
  canvas: [
    { uri: "http://localhost:8080/catalogue/screens/654" }
  ],
  domainContext: {
    tags: [],
	  user: null
  },
  elements: []
}
\end{verbatim}
\doublespacing

@@

\singlespacing
\begin{verbatim}
[
  "http://localhost:8080/catalogue/screens/371",
  "http://localhost:8080/catalogue/screens/24",
  "http://localhost:8080/catalogue/screens/253",
  "http://localhost:8080/catalogue/screens/12"
]
\end{verbatim}
\doublespacing

@@

\singlespacing
\begin{verbatim}
{
  "canvas": [
    { "uri": "http://localhost:8080/catalogue/screens/238" }
  ],
  "elements": [
    { "uri": "http://localhost:8080/catalogue/screens/636" }
  ],
  "domainContext": {
    "tags": [
      {
        "label": { "en-GB": "Amazon" },
        "means": "http://dbpedia.org/page/Amazon.com"
      }
    ],
    "user": "irivera",
  },
  criterion: "reachability"
}
\end{verbatim}
\doublespacing

@@

\singlespacing
\begin{verbatim}
{
  "canvas": [{
    "preconditions": [{
      "label": {"en-gb": "A person working in DERI"},
      "pattern": "?person rdf:type foaf:Person . 
                  ?person foaf:workplaceHomepage http://www.deri.ie/",
      "positive": true,
      "satisfied": false
    }],
    "reachability": false,
    "uri": "http://localhost:8080/catalogue/screens/238"
  }],
  "elements": [{
    "preconditions": [{
      "label": {"en-gb": "A person"},
      "pattern": "?person rdf:type foaf:Person",
      "satisfied": false
    }],
    "reachability": false,
    "uri": "http://localhost:8080/catalogue/screens/636"
  }]
}
\end{verbatim}
\doublespacing

@@

\singlespacing
\begin{verbatim}
{
  "canvas": [{
    "preconditions": [{
      "label": {"en-gb": "A person working in DERI"},
      "pattern": "?person rdf:type foaf:Person . 
                  ?person foaf:workplaceHomepage http://www.deri.ie/",
      "positive": true,
      "satisfied": false
    }],
    "reachability": false,
    "uri": "http://localhost:8080/catalogue/screens/238"
  }],
  "elements": [
    {
      "preconditions": [{
        "label": {"en-gb": "A person"},
        "pattern": "?person rdf:type foaf:Person",
        "satisfied": false
      }],
      "reachability": false,
      "uri": "http://localhost:8080/catalogue/screens/636"
    },
    {
      "preconditions": [],
      "reachability": true,
      "uri": "http://localhost:8080/catalogue/screens/132"
    }
  ]
}
\end{verbatim}
\doublespacing

@@

\singlespacing
\begin{verbatim}
[
  "http://localhost:8080/catalogue/screens/12",
  "http://localhost:8080/catalogue/screens/48",
  "http://localhost:8080/catalogue/forms/9",
]
\end{verbatim}
\doublespacing

@@

\singlespacing
\begin{verbatim}
{
  "screenflows": [],
  "screens": [
    {
      "creationDate": "2009-02-07T09:59:52+0000",
      "creator": "irivera",
      ...,
      "uri": "http://localhost:8080/catalogue/screens/12",
      "version": "1.0"
    },
    {
      "creationDate": "2009-02-07T09:59:52+0000",
      "creator": "irivera",
      ...,
      "uri": "http://localhost:8080/catalogue/screens/12",
      "version": "1.0"
    }
  ],
  "forms": [
    {
      "actions": [
        {
          "name": "init",
          "preconditions": [],
          "uses": []
        },
        {
          "name": "showTable",
          "preconditions": [{
            "id": "list",
            "label": {"en-gb": "A product list"},
            "pattern": "?PList
                        http://www.w3.org/1999/02/22-rdf-syntax-ns#type
                        http://aws.amazon.com/AWSECommerceService#ProductList",
            "positive": true
          }],
          "uses": []
        }
      ],
      ...,
      "uri": "http://localhost:8080/FASTCatalogue/forms/9",
      "version": "1.0"
    },
  ],
  "operators": [],
  "backendservices": []
}
\end{verbatim}
\doublespacing

@@

\begin{description}
	\item[preconditions] Preconditions of the screen.
	\item[postconditions] Postcondition of the screen.
	\item[canvas] The canvas is composed by a list of screens. Only the URI is needed.
	\item[forms] It is a list of forms, such as the list of forms recommended last execution.
	\item[operators] It is a list of operators, such as the list of operators recommended last execution.
	\item[backendservices] It is a list of back-end services, such as the list of back-end services recommended last execution.
	\item[domainContext] The domain context contains a list of tags and a user.
	\item[pipes] List of pipes for the connection between screen components.
	\item[selectedItem] URI of a screen component from the canvas.
\end{description}

@@

\singlespacing
\begin{verbatim}
{
  "preconditions": [{
    "id": "Searchcriteria_1",
    "label": {"en-gb": "A search criteria"},
    "pattern": "?F
                http://www.w3.org/1999/02/22-rdf-syntax-ns#type
                http://aws.amazon.com/AWSECommerceService#SearchCriteria",
    "positive": true,
  }],
  "postconditions": [],
  "canvas": [
    { "uri": "http://localhost:8080/catalogue/forms/1" },
    { "uri": "http://localhost:8080/catalogue/services/1" }
  ],
  "forms": [],
  "operators": [],
  "backendservices": [],
  "domainContext": {
    "tags": [],
    "user": null
  },
  "pipes": [
    {
      "from": {
        "buildingblock": "http://localhost:8080/catalogue/services/1",
        "condition": "list"
      },
      "to": {
        "action": "showTable",
        "buildingblock": "http://localhost:8080/catalogue/forms/1",
        "condition": "list"
      }
    }
  ],
  "selectedItem": "http://localhost:8080/catalogue/forms/1"
}
\end{verbatim}
\doublespacing

@@

\singlespacing
\begin{verbatim}
{
  "backendservices": [],
  "canvas": [
    {
      "actions": [{
        "name": "search",
        "preconditions": [{
          "id": "filter",
          "label": {"en-gb": "A search criteria"},
          "pattern": "?F 
                      http://www.w3.org/1999/02/22-rdf-syntax-ns#type
                      http://aws.amazon.com/AWSECommerceService#SearchCriteria",
          "positive": true,
          "satisfied": false
        }],
        "satisfied": false,
        "uses": []
      }],
      "reachability": false,
      "uri": "http://localhost:8080/catalogue/services/1"
    },
    {
      "actions": [
        {
          "name": "init",
          "preconditions": [],
          "satisfied": true,
          "uses": []
        },
        {
          "name": "showTable",
          "preconditions": [{
            "id": "list",
            "label": {"en-gb": "A product list"},
            "pattern": "?PList
                        http://www.w3.org/1999/02/22-rdf-syntax-ns#type
                        http://aws.amazon.com/AWSECommerceService#ProductList",
            "positive": true,
            "satisfied": false
          }],
          "satisfied": false,
          "uses": []
        }
      ],
      "reachability": true,
      "uri": "http://localhost:8080/catalogue/forms/1"
    }
  ],
  "connections": [
    {
      "from": {
        "buildingblock": null,
        "condition": "Searchcriteria_1"
      },
      "to": {
        "action": "search",
        "buildingblock": "http://localhost:8080/catalogue/services/1",
        "condition": "filter"
      }
    },
  ],
  "forms": [],
  "operators": [],
  "pipes": [
    {
      "from": {
        "buildingblock": "http://localhost:8080/catalogue/services/1",
        "condition": "list"
      },
      "satisfied": true,
      "to": {
        "action": "showTable",
        "buildingblock": "http://localhost:8080/catalogue/forms/1",
        "condition": "list"
      }
    }
  ],
  "postconditions": []
}
\end{verbatim}
\doublespacing

@@

Request
\singlespacing
\begin{verbatim}
{
  "goal": "http://localhost:8080/catalogue/screens/35",
  "canvas": [
    { "uri": "http://localhost:8080/catalogue/screens/56" },
    { "uri": "http://localhost:8080/catalogue/screens/85" }
  ],
  "page": 1,
  "per_page": 10 
}
\end{verbatim}
\doublespacing

Response
\singlespacing
\begin{verbatim}
[
  [
    "http://localhost:8080/catalogue/screens/13",
    "http://localhost:8080/catalogue/screens/23"
  ],
  [
    "http://localhost:8080/catalogue/screens/79",
    "http://localhost:8080/catalogue/screens/37",
    "http://localhost:8080/catalogue/screens/14"
  ],
  [
    "http://localhost:8080/catalogue/screens/16",
    "http://localhost:8080/catalogue/screens/44",
    "http://localhost:8080/catalogue/screens/32"
  ]
]
\end{verbatim}
\doublespacing

@@

\singlespacing
\begin{verbatim}
{
  "code": "http://url.com/.../code.js",
  "creationDate": "2009-04-20T17:00:00+0100",
  "creator": "http://www.fabio.es/",
  "description": {"en-gb": "This is a description of the building block"},
  "tags": {
    "tags": [
      "ebay",
      "amazon",
    ],
    "user": <String> // not defined yet
  },
  "homepage": "http://www.homepage.ie/",
  "icon": "http://url.com/images/icon.png",
  "id": "Id of the resource",
  "label": {"en-gb": "Label or title of the building block"},
  "name": "Amazon Item to Ebay Filter",
  "rights": "http://creativecommons.org/",
  "screenshot": "http://www.deri.ie/eBayList-screenshot.jpg",
  "type": "type of the building block", // screenflow, screen, form, operator y resource
  "uri": "http://localhost:8080/catalogue/screens/525",
  "version": "1.0"
}
\end{verbatim}
\doublespacing

@@

\singlespacing
\begin{verbatim}
{
  <GENERIC BUILDING BLOCK JSON>,
  "contains": [
    "http://purl.oclc.org/fast/ontology/gadget#Screen1257860772723",
    "http://purl.oclc.org/fast/ontology/gadget#Screen1257860720035",
  ],
}
\end{verbatim}
\doublespacing

>>>>

\begin{itemize}
	\item Section~\ref{sec:installation_guide}. Installation Guide describes a set of steps to be followed in order to install and execute the FAST Catalogue. Also some configuration instructions are specified.
	\item Section~\ref{sub:linked_data}. Content Negotiation states how the FAST Catalogue has adopted several of the content negotiation principles.
	\item Section~\ref{sec:restful_catalogue_api}. RESTful Catalogue API has been intensively extended and modified in order to  reflect all the new functionality and how every request or response is constructed. Some of the most important features added in this iteration are:
	\begin{itemize}
		\item support for form elements, operators and back-end services (see Section ...),
		\item convenience operations for recommendation and checking satisfaction and reachability for form elements, operators and back-end services (see Section ...),
		\item and, last but not least, support for Screen planning (see Section~\ref{sub:planning}).
	\end{itemize}
	\item Several appendixes have been added with the JSON structure of every building block the Catalogue can deal with.
	\item Appendix A. Last year an evaluation to choose the best technology for the Catalogue was done. It was not included in any formal deliverable, so this year it has been documented as an appendix.
\end{itemize}

@@

Note that it is also possible to get the compiled WAR file directly from the SVN server. This file can be located at \url{https://svn.forge.morfeo-project.org/fast-fp7project/distribution/catalogue}.

@@

Independently the type of repository, the parameter \emph{serverURL} needs to take the value of the URL where the FAST Catalogue instance has been deployed. If you are testing the application in your machine, it may be something like \url{http://catalogueURL/FASTCatalogue}.

@@

It is recommended to check if the FAST Catalogue has been successfully installed. To do that, a simple HTTP request, using a Web browser, can be sent to the URL the Catalogue is deployed, and specifying a type of resource such as Screen. The URL would be similar to \url{http://catalogueURL/FASTCatalogue/screens}. Depending on the variant chosen, the response may be different. For JSON, the response should be \verb|[]|, but in HTML the message \verb|No screens found.| should be shown.

@@

\singlespacing
\begin{verbatim}
{
  "canvas": [
    { "uri": "http://catalogueURL/catalogue/screens/238" },
    { "uri": "http://catalogueURL/catalogue/screens/323" }
  ],
  "elements": [
    { "uri": "http://catalogueURL/catalogue/screens/636" }
  ],
  "domainContext": {
    "tags": [
      {
        "label": { "en-GB": "Amazon" },
        "means": "http://dbpedia.org/page/Amazon.com"
      }
    ],
    "user": "irivera",
  },
  "criterion": "reachability"
}
\end{verbatim}
\doublespacing

@@

\subsection{Linked Data} % (fold)
\label{sub:linked_data}

Apart from serving as the back-end system for the Gadget Visual Storyboard or GVS, the catalogue publishes all FAST building blocks as linked data following the four rules or principles dictated in \cite{bernersLee2006linkedData}. Hence, building blocks are identified by URIs, concretely HTTP URIs so anyone can look them up. The data obtained for these building blocks is served in different standard formats such as JSON (GVS communication), RDF/XML, Turtle, or even HTML+RDFa as a human-readable version. And as the forth rule states, these building blocks links to other resources on the web. Moreover, principles and best practices from \cite{berrueta2008} and \cite{sauermann2008cool_uris} have been followed for the publication and identification of the building blocks. The mechanism to allow its publication/identification in different formats is called Content Negotiation.

@@

In summary, the basic idea of content negotiation, as stated in the \cite{http1.1}, is to serve the best variant for a resource, taking into account what variants are available, what variants the server may prefer to serve, what the client can accept, and with which preferences: in HTTP, this is done by the client which may send, in its request, Accept headers (Accept, Accept-Language and Accept-Encoding), to communicate its capabilities and preferences in Format, Language and Encoding, respectively.

In fact, what the catalogue really does is "format negotiation" since the alternate representationos are just based on the selection of the media type, through the \emph{Accept} header, but does not consider different languages or encoding types. The formats supported are JSON, RDF/XML, Turtle and HTML+RDFa. Even though the \emph{Accept} header is desired, these different representations can be retrieved by adding the format at the end of the resource URI. For instance, to get the RDF representation of the screen 457, performing a GET HTTP request to <catalogue\_url>/screens/457.rdf will serve the information in RDF/XML.

@@

To create a new screen, a POST request is send to the catalogue server, concretely to http://catalogueURL/screens, including the JSON representation of the screen in the body of the request:

@@

\singlespacing
\begin{verbatim}
{
  "code": "http://demo.fast.morfeo-project.org/code/amazonList.js",
  "creationDate": "2010-01-26T17:01:13+0000",
  "creator": "irivera",
  "description": {"en-gb": "Please fill the description..."},
  "homepage": "http://fast.morfeo-project.eu/",
  "icon": "http://demo.fast.morfeo-project.org/images/amazonList.png",
  "id": "28",
  "label": {"en-gb": "Prueba1"},
  "name": "ProductList",
  "postconditions": [
    [
      {
        "id": "item",
        "label": { "en-gb": "An item" },
        "pattern": "?I
                    http://www.w3.org/1999/02/22-rdf-syntax-ns#type
                    http://aws.amazon.com/AWSECommerceService#Item",
        "positive": "true"
      }
    ]
  ],
  "preconditions": [
    [
      {
        "id": "filter",
        "label": { "en-gb": "A search criteria" },
        "pattern": "?F
                    http://www.w3.org/1999/02/22-rdf-syntax-ns#type
                    http://aws.amazon.com/AWSECommerceService#SearchCriteria",
        "positive": "true"
      }
    ]
  ],
  "rights": "http://creativecommons.org/",
  "screenshot": "http://demo.fast.morfeo-project.org/images/amazonProductList.png",
  "tags": [{"label": {"en-gb": "amazon"}}],
  "type": "screen",
  "uri": "http://catalogueURL/catalogue/screens/28",
  "version": "0.1"
}
\end{verbatim}
\doublespacing

@@

\singlespacing
\begin{verbatim}
[
  {
    "code": "http://demo.fast.morfeo-project.org/code/amazonList.js",
    "creationDate": "2010-01-26T17:01:13+0000",
    "creator": "irivera",
    "description": {"en-gb": "Please fill the description..."},
    "homepage": "http://fast.morfeo-project.eu/",
    "icon": "http://demo.fast.morfeo-project.org/images/amazonList.png",
    "id": "28",
    "label": {"en-gb": "Prueba1"},
    "name": "ProductList",
    "postconditions": [
      [
        {
          "id": "item",
          "label": { "en-gb": "An item" },
          "pattern": "?I
                      http://www.w3.org/1999/02/22-rdf-syntax-ns#type
                      http://aws.amazon.com/AWSECommerceService#Item",
          "positive": "true"
        }
      ]
    ],
    "preconditions": [
      [
        {
          "id": "filter",
          "label": { "en-gb": "A search criteria" },
          "pattern": "?F
                      http://www.w3.org/1999/02/22-rdf-syntax-ns#type
                      http://aws.amazon.com/AWSECommerceService#SearchCriteria",
          "positive": "true"
        }
      ]
    ],
    "rights": "http://creativecommons.org/",
    "screenshot": "http://demo.fast.morfeo-project.org/images/amazonProductList.png",
    "tags": [{"label": {"en-gb": "amazon"}}],
    "type": "screen",
    "uri": "http://catalogueURL/catalogue/screens/28",
    "version": "0.1"
  },
  {
    "creationDate": "2009-02-07T09:59:52+0000",
    "creator": "fabio",
    ...,
	  "uri": "http://catalogueURL/catalogue/screens/14",
    "version": "1.0"
  },
  {
    "creationDate": "2009-02-07T09:59:52+0000",
    "creator": "javier",
    ...,
	  "uri": "http://catalogueURL/catalogue/screens/564",
    "version": "1.0"
  }
]
\end{verbatim}
\doublespacing

@@

Following is shown an example of usage of this operation considering a canvas with the screen \texttt{http://catalogueURL/catalogue/screens/654}.

\singlespacing
\begin{verbatim}
{
  canvas: [
    { uri: "http://catalogueURL/catalogue/screens/654" }
  ],
  domainContext: {
    tags: [],
	  user: null
  },
  elements: []
}
\end{verbatim}
\doublespacing

@@

\singlespacing
\begin{verbatim}
[
  "http://catalogueURL/catalogue/screens/371",
  "http://catalogueURL/catalogue/screens/24",
  "http://catalogueURL/catalogue/screens/253",
  "http://catalogueURL/catalogue/screens/12"
]
\end{verbatim}
\doublespacing

@@

\singlespacing
\begin{verbatim}
{
  "canvas": [
    { "uri": "http://catalogueURL/catalogue/screens/238" }
  ],
  "elements": [
    { "uri": "http://catalogueURL/catalogue/screens/636" }
  ],
  "domainContext": {
    "tags": [
      {
        "label": { "en-GB": "Amazon" },
        "means": "http://dbpedia.org/page/Amazon.com"
      }
    ],
    "user": "irivera",
  },
  criterion: "reachability"
}
\end{verbatim}
\doublespacing

@@

\singlespacing
\begin{verbatim}
{
  "canvas": [{
    "preconditions": [{
      "label": {"en-gb": "A person working in DERI"},
      "pattern": "?person rdf:type foaf:Person . 
                  ?person foaf:workplaceHomepage http://www.deri.ie/",
      "positive": true,
      "satisfied": false
    }],
    "reachability": false,
    "uri": "http://catalogueURL/catalogue/screens/238"
  }],
  "elements": [{
    "preconditions": [{
      "label": {"en-gb": "A person"},
      "pattern": "?person rdf:type foaf:Person",
      "satisfied": false
    }],
    "reachability": false,
    "uri": "http://catalogueURL/catalogue/screens/636"
  }]
}
\end{verbatim}
\doublespacing

@@

\singlespacing
\begin{verbatim}
{
  "canvas": [{
    "preconditions": [{
      "label": {"en-gb": "A person working in DERI"},
      "pattern": "?person rdf:type foaf:Person . 
                  ?person foaf:workplaceHomepage http://www.deri.ie/",
      "positive": true,
      "satisfied": false
    }],
    "reachability": false,
    "uri": "http://catalogueURL/catalogue/screens/238"
  }],
  "elements": [
    {
      "preconditions": [{
        "label": {"en-gb": "A person"},
        "pattern": "?person rdf:type foaf:Person",
        "satisfied": false
      }],
      "reachability": false,
      "uri": "http://catalogueURL/catalogue/screens/636"
    },
    {
      "preconditions": [],
      "reachability": true,
      "uri": "http://catalogueURL/catalogue/screens/132"
    }
  ]
}
\end{verbatim}
\doublespacing

@@

\singlespacing
\begin{verbatim}
[
  "http://catalogueURL/catalogue/screens/12",
  "http://catalogueURL/catalogue/screens/48",
  "http://catalogueURL/catalogue/forms/9",
]
\end{verbatim}
\doublespacing

@@

\singlespacing
\begin{verbatim}
{
  "screenflows": [],
  "screens": [
    {
      "creationDate": "2009-02-07T09:59:52+0000",
      "creator": "irivera",
      ...,
      "uri": "http://catalogueURL/catalogue/screens/12",
      "version": "1.0"
    },
    {
      "creationDate": "2009-02-07T09:59:52+0000",
      "creator": "irivera",
      ...,
      "uri": "http://catalogueURL/catalogue/screens/12",
      "version": "1.0"
    }
  ],
  "forms": [
    {
      "actions": [
        {
          "name": "init",
          "preconditions": [],
          "uses": []
        },
        {
          "name": "showTable",
          "preconditions": [{
            "id": "list",
            "label": {"en-gb": "A product list"},
            "pattern": "?PList
                        http://www.w3.org/1999/02/22-rdf-syntax-ns#type
                        http://aws.amazon.com/AWSECommerceService#ProductList",
            "positive": true
          }],
          "uses": []
        }
      ],
      ...,
      "uri": "http://catalogueURL/FASTCatalogue/forms/9",
      "version": "1.0"
    },
  ],
  "operators": [],
  "backendservices": []
}
\end{verbatim}
\doublespacing

@@

\begin{description}
	\item[preconditions] Preconditions of the screen.
	\item[postconditions] Postcondition of the screen.
	\item[canvas] The canvas is composed by a list of screens. Only the URI is needed.
	\item[forms] It is a list of forms, such as the list of forms recommended last execution.
	\item[operators] It is a list of operators, such as the list of operators recommended last execution.
	\item[backendservices] It is a list of back-end services, such as the list of back-end services recommended last execution.
	\item[search] Boolean indicating if forms/operators/services are required to be looked for. If \emph{false} the operation performed is just a check. If missed, it will act as \emph{true}.
	\item[domainContext] The domain context contains a list of tags and a user.
	\item[pipes] List of pipes for the connection between screen components.
	\item[selectedItem] URI of a screen component from the canvas.
\end{description}

@@

\singlespacing
\begin{verbatim}
{
  "preconditions": [{
    "id": "Searchcriteria_1",
    "label": {"en-gb": "A search criteria"},
    "pattern": "?F
                http://www.w3.org/1999/02/22-rdf-syntax-ns#type
                http://aws.amazon.com/AWSECommerceService#SearchCriteria",
    "positive": true,
  }],
  "postconditions": [],
  "canvas": [
    { "uri": "http://catalogueURL/catalogue/forms/1" },
    { "uri": "http://catalogueURL/catalogue/services/1" }
  ],
  "forms": [],
  "operators": [],
  "backendservices": [],
  "search": true,
  "domainContext": {
    "tags": [],
    "user": null
  },
  "pipes": [
    {
      "from": {
        "buildingblock": "http://catalogueURL/catalogue/services/1",
        "condition": "list"
      },
      "to": {
        "action": "showTable",
        "buildingblock": "http://catalogueURL/catalogue/forms/1",
        "condition": "list"
      }
    }
  ],
  "selectedItem": "http://catalogueURL/catalogue/forms/1"
}
\end{verbatim}
\doublespacing

@@

\singlespacing
\begin{verbatim}
{
  "backendservices": [],
  "canvas": [
    {
      "actions": [{
        "name": "search",
        "preconditions": [{
          "id": "filter",
          "label": {"en-gb": "A search criteria"},
          "pattern": "?F 
                      http://www.w3.org/1999/02/22-rdf-syntax-ns#type
                      http://aws.amazon.com/AWSECommerceService#SearchCriteria",
          "positive": true,
          "satisfied": false
        }],
        "satisfied": false,
        "uses": []
      }],
      "reachability": false,
      "uri": "http://catalogueURL/catalogue/services/1"
    },
    {
      "actions": [
        {
          "name": "init",
          "preconditions": [],
          "satisfied": true,
          "uses": []
        },
        {
          "name": "showTable",
          "preconditions": [{
            "id": "list",
            "label": {"en-gb": "A product list"},
            "pattern": "?PList
                        http://www.w3.org/1999/02/22-rdf-syntax-ns#type
                        http://aws.amazon.com/AWSECommerceService#ProductList",
            "positive": true,
            "satisfied": false
          }],
          "satisfied": false,
          "uses": []
        }
      ],
      "reachability": true,
      "uri": "http://catalogueURL/catalogue/forms/1"
    }
  ],
  "connections": [
    {
      "from": {
        "buildingblock": null,
        "condition": "Searchcriteria_1"
      },
      "to": {
        "action": "search",
        "buildingblock": "http://catalogueURL/catalogue/services/1",
        "condition": "filter"
      }
    },
  ],
  "forms": [],
  "operators": [],
  "pipes": [
    {
      "from": {
        "buildingblock": "http://catalogueURL/catalogue/services/1",
        "condition": "list"
      },
      "satisfied": true,
      "to": {
        "action": "showTable",
        "buildingblock": "http://catalogueURL/catalogue/forms/1",
        "condition": "list"
      }
    }
  ],
  "postconditions": []
}
\end{verbatim}
\doublespacing

@@

Request
\singlespacing
\begin{verbatim}
{
  "goal": "http://catalogueURL/catalogue/screens/35",
  "canvas": [
    { "uri": "http://catalogueURL/catalogue/screens/56" },
    { "uri": "http://catalogueURL/catalogue/screens/85" }
  ],
  "page": 1,
  "per_page": 10 
}
\end{verbatim}
\doublespacing

Response
\singlespacing
\begin{verbatim}
[
  [
    "http://catalogueURL/catalogue/screens/13",
    "http://catalogueURL/catalogue/screens/23"
  ],
  [
    "http://catalogueURL/catalogue/screens/79",
    "http://catalogueURL/catalogue/screens/37",
    "http://catalogueURL/catalogue/screens/14"
  ],
  [
    "http://catalogueURL/catalogue/screens/16",
    "http://catalogueURL/catalogue/screens/44",
    "http://catalogueURL/catalogue/screens/32"
  ]
]
\end{verbatim}
\doublespacing

@@

\singlespacing
\begin{verbatim}
{
  "code": "http://url.com/.../code.js",
  "creationDate": "2009-04-20T17:00:00+0100",
  "creator": "username",
  "description": {"en-gb": "This is a description of the building block"},
    "tags":[
      {
        "label":{"en-gb":"Amazon"},
        "means":"http://dbpedia.org/page/Amazon.com"
      },
      {
        "label":{"en-gb":"eBay"},
        "means":"http://dbpedia.org/page/Ebay"
      }
    ],
  "homepage": "http://url.com/.../homepage",
  "icon": "http://url.com/images/.../icon.png",
  "id": "Id of the building block", // i.e. 3545
  "label": {"en-gb": "Label or title of the building block"},
  "name": "User-friendly name of the building block",
  "rights": "http://creativecommons.org/",
  "screenshot": "http://url.com/.../screenshot.jpg",
  "type": "type of the building block", // screenflow, screen, form, operator or resource
  "uri": "http://url.com/screens/525",
  "version": "1.0"
}
\end{verbatim}
\doublespacing

@@

\singlespacing
\begin{verbatim}
{
  <GENERIC BUILDING BLOCK JSON>,
  "contains": [
    "http://url.com/screens/72723",
    "http://url.com/screens/20035",
  ],
}
\end{verbatim}
\doublespacing
